Cover Letter: Cudele

### 2018-01-07 paper/cover_letter.tex
misc touch ups to address #48
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We thank the reviewers for their hard work and genuinely helpful suggestions.
In addition to this cover letter, we have posted a PDF online explicitly
showing additions in \textcolor{red}{\textbf{red}} and deletions in
\textcolor{blue}{\textbf{blue}}. Three issues were common across reviewer
feedback; Reviewer 1 and 3's comments are addressed in issues II and III,
Reviewer 2's comments are addressed in issues I and III, and Reviewer 4's
comments are addressed in issues I and II.

@@

We apologize for the omission of experimental setup and source code details.
We made artifacts available online for all experiments in the paper. For the
experimental setup, we describe the cluster setup (hardware, software, etc.) in
Section~{\S}V.  We have also made the infrastructure code available and added
links after each figure to show exactly how experiments are run.  This
infrastructure code contains scripts to deploy the system, run experiments, and
gather results.  This process follows the Popper
Convention\footnote{http://falsifiable.us/}~\cite{jimenez_popper_2016}, which
aims to make research reproducible.  We also made the source code available
online and a link is provided in a reference in Section~{\S}V. Finally, we add
details about which tools and classes we modified in Section~{\S}IV to address
Reviewer 1's questions about the framework implementation.

>>>>

We thank the reviewers for their hard work and genuinely helpful suggestions.
In addition to this cover letter, we have posted a PDF online explicitly
showing additions in \textcolor{blue}{\textbf{blue}} and deletions in
\textcolor{red}{\textbf{red}}. Three issues were common across reviewer
feedback; Reviewer 1 and 3's comments are addressed in issues II and III,
Reviewer 2's comments are addressed in issues I and III, and Reviewer 4's
comments are addressed in issues I and II.

@@

We apologize for the omission of experimental setup and source code details.
We made artifacts available online for all experiments in the paper. For the
experimental setup, we describe the cluster setup (hardware, software, etc.) in
Section~{\S}V.  We have also made the infrastructure code available and added
links after each figure to show exactly how experiments are run.  This
infrastructure code contains scripts to deploy the system, run experiments, and
gather results.  This process follows the \href{Popper
Convention}{http://falsifiable.us/}~\cite{jimenez_popper_2016}, which aims to
make research reproducible.  We also made the source code available online and
a link is provided in Section~{\S}V. Finally, we add details about which tools
and classes we modified in Section~{\S}IV to address Reviewer 1's questions
about the framework implementation.

### 2018-01-07 paper/sections/5_implementation.tex
misc touch ups to address #48
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In CephFS, the inode cache reduces the number of RPCs between clients and
metadata servers. Without contention clients can resolve metadata reads locally
thus reducing the number of operations ({\it e.g.}, \texttt{lookup()}s).  For
example, if a client or metadata server is not caching the directory inode, all
creates within that directory will result in a lookup and a create request. If
the directory inode is cached then only the create needs to be sent.  The size
of the inode cache is configurable so as not to saturate the memory on the
metadata server -- inodes in CephFS are about 1400
bytes~\cite{docs:cephinternalds}.  The inode cache has code for manipulating
inode numbers, such as pre-allocating inodes to clients. \textbf{In
Cudele},Nonvolatile Apply uses the internal inode cache code to allocate inodes
to clients that decouple parts of the namespace and to skip inodes used by the
client at merge time.

>>>>

In CephFS, the inode cache reduces the number of RPCs between clients and
metadata servers. Without contention clients can resolve metadata reads locally
thus reducing the number of operations ({\it e.g.}, \texttt{lookup()}s).  For
example, if a client or metadata server is not caching the directory inode, all
creates within that directory will result in a lookup and a create request. If
the directory inode is cached then only the create needs to be sent.  The size
of the inode cache is configurable so as not to saturate the memory on the
metadata server -- inodes in CephFS are about 1400
bytes~\cite{docs:cephinternals}.  The inode cache has code for manipulating
inode numbers, such as pre-allocating inodes to clients. \textbf{ In
Cudele}, Nonvolatile Apply uses the internal inode cache code to allocate inodes
to clients that decouple parts of the namespace and to skip inodes used by the
client at merge time.
